\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-14 4-1-basic.Rmd
still tinkering with glyph map

```{r basic-manip, out.width="70%", fig.cap="A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020). An inset (top left) showing detail is the station Cobar. The mothly trend is similar at all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations."}
knitr::include_graphics(here::here("figures/basic-manip.png"))
```

>>>>

```{r basic-manip, out.width="90%", fig.cap="A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020). An inset (top left) showing detail is the station Cobar (highlighted by black rectangle). The mothly trend is similar at all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations."}
knitr::include_graphics(here::here("figures/basic-manip.png"))
```

### 2022-06-14 jss/cubble-jss.tex
still tinkering with glyph map

{\centering \includegraphics[width=0.7\linewidth]{../figures/basic-manip}

@@

\caption[A glyph map of the average maximum temperature by month of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020)]{A glyph map of the average maximum temperature by month of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020). An inset (top left) showing detail is the station Cobar. The mothly trend is similar at all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}

>>>>

{\centering \includegraphics[width=0.9\linewidth]{../figures/basic-manip}

@@

\caption[A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020)]{A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020). An inset (top left) showing detail is the station Cobar (highlighted by black rectangle). The mothly trend is similar at all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}
